Geometric models reveal the hidden structure of conceptual knowledge

### 2023-01-26 paper/main.tex
added stats for knowledge estimates, recompiled

Of course, even though the timecourses in
Figure~\ref{fig:knowledge-timeseries}A and C provide detailed
\textit{estimates} about participants' knowlege, those estimates are only
\textit{useful} to the extent that they accurately reflect what participants
actually know. As one sanity check, we anticipated that the knowledge estimates
should show a content-specific ``boost'' in participants' knowledge after
watching each lecture. In other words, if participants learn about each
lecture's content when they watch each lecture, the knowledge estimates should
reflect that. After watching the \textit{Four Fundamental Forces} lecture,
participants should show more knowledge for the content of that lecture than
they had before, and that knowledge should persist for the remainder of the
experiment. Specifically, knowledge about that lecture's content should be
relatively low when estimated using Quiz 1 responses, but should increase when
estimated using Quiz 2 or 3 responses (Fig.~\ref{fig:knowledge-timeseries}B).
Indeed, we found that participants' estimated knowledge about the content of
the \textit{Four Fundamental Forces} was substantially higher on Quiz 2 versus
Quiz 1 ($t(XX) = XX, p = XX$) and on Quiz 3 versus Quiz 1 ($t(XX) = XX, p =
XX$). We found no reliable differences in estimated knowledge about that
lecture's content on Quiz 2 versus 3 ($t(XX) = XX, p = XX$). Similarly, we
hypothesized (and subsequently confirmed) that participants should show more
estimated knowledge about the content of the \textit{Birth of Stars} lecture
after (versus before) watching it (Fig.~\ref{fig:knowledge-timeseries}D).
Specifically, since participants watched that lecture after taking Quiz 2 (but
before Quiz 3), we hypothesized that their knowledge estimates should be
relatively low on Quizzes 1 and 2, but should show a ``boost'' on Quiz 3.
Consistent with this prediction, we found no reliable differences in estimated
knowledge about the \textit{Birth of Stars} lecture content on Quizzes 1 versus
2 ($t(XX) = XX, p = XX$), but the estimated knowledge was substantially higher
on Quiz 3 versus 2 ($t(XX) = XX, p = XX$) and Quiz 3 versus 1 ($t(XX) = XX, p =
XX$).

@@

\begin{figure}[tp]
    \centering
    \includegraphics[width=\textwidth]{figs/held-out-question-analyses}

>>>>

Of course, even though the timecourses in
Figure~\ref{fig:knowledge-timeseries}A and C provide detailed
\textit{estimates} about participants' knowlege, those estimates are only
\textit{useful} to the extent that they accurately reflect what participants
actually know. As one sanity check, we anticipated that the knowledge estimates
should show a content-specific ``boost'' in participants' knowledge after
watching each lecture. In other words, if participants learn about each
lecture's content when they watch each lecture, the knowledge estimates should
reflect that. After watching the \textit{Four Fundamental Forces} lecture,
participants should show more knowledge for the content of that lecture than
they had before, and that knowledge should persist for the remainder of the
experiment. Specifically, knowledge about that lecture's content should be
relatively low when estimated using Quiz 1 responses, but should increase when
estimated using Quiz 2 or 3 responses (Fig.~\ref{fig:knowledge-timeseries}B).
Indeed, we found that participants' estimated knowledge about the content of
the \textit{Four Fundamental Forces} was substantially higher on Quiz 2 versus
Quiz 1 ($t(49) = 8.764, p < 0.001$) and on Quiz 3 versus Quiz 1 ($t(49) = 10.519, p <
0.001$). We found no reliable differences in estimated knowledge about that
lecture's content on Quiz 2 versus 3 ($t(49) = 0.160, p = 0.874$). Similarly, we
hypothesized (and subsequently confirmed) that participants should show more
estimated knowledge about the content of the \textit{Birth of Stars} lecture
after (versus before) watching it (Fig.~\ref{fig:knowledge-timeseries}D).
Specifically, since participants watched that lecture after taking Quiz 2 (but
before Quiz 3), we hypothesized that their knowledge estimates should be
relatively low on Quizzes 1 and 2, but should show a ``boost'' on Quiz 3.
Consistent with this prediction, we found no reliable differences in estimated
knowledge about the \textit{Birth of Stars} lecture content on Quizzes 1 versus
2 ($t(49) = 1.013, p = 0.316$), but the estimated knowledge was substantially higher
on Quiz 3 versus 2 ($t(49) = 10.561, p < 0.001$) and Quiz 3 versus 1 ($t(49) = 8.969, p <
0.001$).

@@

\begin{figure}[tp]
    \centering
    \includegraphics[width=\textwidth]{figs/held-out-question-analysis}
